---
title: "Blank Storyboard Template"
author: "Nobody"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}

# this line specifies options for default options for all R Chunks
knitr::opts_chunk$set(echo=F)

# suppress scientific notation
options(scipen=100,
        getSymbols.warning4.0 = FALSE)

# install helper package (pacman), if needed
if (!require("pacman")) install.packages("pacman", repos = "http://lib.stat.cmu.edu/R/CRAN/")

# install and load required packages
# pacman should be first package in parentheses and then list others
pacman::p_load(pacman, tidyverse, ggthemes, magrittr, lubridate, tidyquant, highcharter,
               flexdashboard,knitr, RColorBrewer, dygraphs, gridExtra)

# remove # in front of p_loaded if needed
# p_loaded()

```

### Description for Panel 1

```{r data mgmt and plot code for panel 1}


```

***

Text after the `***` appears in right panel, next to plot panel.

Other descriptive information, insights.

***
 
### Description for Panel 2

```{r data mgmt and plot code for panel 2}


```

***

Text after the `***` appears in right panel, next to plot panel.

Other descriptive information, insights.

Caption for Summary Table

```{r summary table for panel 2}

# Adding a chunk like this with a table
# would place a summary table in the right panel next to the plot

```

***

Other descriptive information, insights, or a summary table can be included here.

Text after the `***` appears in right panel, next to plot panel.

This text would appear below summary table

Other descriptive information, insights.

***

### Description for Panel 3

```{r data mgmt and plot code for panel 3}


```

***

Text after the `***` appears in right panel, next to plot panel.

Other descriptive information, insights.